An Abstraction-based Approach to Network Synthesis

### 2016-11-03 paper/abstraction/paper.tex
added incremental section, start abstract analysis

\section{Analysis}
\label{sec:analysis}

%\para{Semantics}

%We give a semantics to RIR programs using sets of ranked paths. Each path constraint $r_1 \Prefer \dots \Prefer r_j$ denotes a set of ranked network paths. A network path is a topologically valid string of abstract locations $l_1 l_2 \dots l_k$. We use the notation $\abs{p}$ to denote the length of the path $p$. A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression. Paths are ranked lexicographically according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length. Lower ranks indicate \emph{more} preferred paths. More formally, a path $p$ has rank:
%$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
%%
%The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
%%
%For any source $s$ and destination $d$, \sysname will send traffic along the highest ranked available path from $s$ to $d$.

\subsection{Other properties}
\label{sec:property-checking}

\begin{easylist}[itemize]
& K-disjoint path analysis
&& Useful for aggregation safety (black holes) & reachability
&& Inference rules as an abstract interpretation using Z3
\end{easylist}

@@

%\subsection{Aggregation-safety analysis}
%\label{sec:agg-safety}

%As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur. Determining when this can happen requires knowledge, not only of the topology, but also of the policy. For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated. If that one link fails, a black hole might be introduced.
%%
%Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.%

%We view the aggregation problem as a variant of the min-cut problem in the PGIR. Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point. The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
%%%

%Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix's origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topology edge along the chosen path, and $iii)$ repeat until no such path exists.
%Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.%
%

%Recall the datacenter example from \S\ref{sec:motivation}, with the policy
%\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}. Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first and would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

%\subsection{Abstract BGP}
%\label{sec:abgp}
%The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).

%\para{From PGIR to ABGP}

%\newcommand{\highlight}[1]{%
%  \colorbox{red!50}{$\displaystyle#1$}}
%\newcommand{\Router}[1]{\KW{Router} #1:}
%\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
%\newcommand{\PEER}{\texttt{peer}}
%\newcommand{\COMM}{\texttt{comm}}
%\newcommand{\MED}{\texttt{MED}}
%\newcommand{\Arrow}{\ensuremath{\leftarrow}}%

%\begin{figure}[t!]
%\begin{code}
%  \Router{A}
%    Match \PEER=C, \COMM=(3,2)
%      Export \COMM \Arrow (4,2),
%             \MED \Arrow 80, \PEER \Arrow W
%  \Router{B}
%    Match \PEER = C, \COMM = (-,2) or (3,2)
%      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
%             \MED \Arrow 81, \PEER \Arrow W
%  \Router{C}
%    Match[LP=99] \PEER = E, \COMM = (-,2)
%      Export \COMM \Arrow (-,2), \PEER \Arrow B
%    Match \PEER = D, \COMM = (2,2)
%      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
%  \Router{D}
%    Match \REGEX{X + Y}
%      Export \COMM \Arrow (2,2), \PEER \Arrow C
%  \Router{E}
%    Match \REGEX{Z}
%      Export \COMM \Arrow (-,2), \PEER \Arrow C
%  \end{code}
%  \vspace{-2em}
%  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
%  \vspace{-1em}
%\end{figure}

>>>>

\section{Abstract Analysis}
\label{sec:analysis}

In the previous section we saw that \sysname can synthesize correct device configurations by operating directly over the abstract representation. However, in practice operators would often like to reason about other properties about their network. In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes. Answering questions about the number of disjoint paths allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers). An important point is that the analysis takes place over the structure of the product graph, and so takes both the topology and routing policy into account.

\subsection{Abstract k-disjoint paths}
\label{sec:property-checking}

@@

In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.

The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location. More specifically, we maintain facts of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k) 
\end{array} \]
\noindent
%
Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label in the nesting for each pod scope in the network abstraction hierarchy. So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label. The value $j$ tells us the number of concrete nodes in the group that are reachable, and the value $k$ tells us the number of disjoint paths to each of the $j$ nodes such that all $j*k$ paths are disjoint.
